\textbf{Seasonal Dynamics of Epiphytic Microbial Communities on Marine Macrophyte Surfaces}

### 2020-03-02 submission/manuscript.Rmd
Desulfobacterota removal checked.

Observed highest richness values for *Caulerpa cylindracea* (invaded and noninvaded), middle for *Cymodocea nodosa* and lowest for seawater derived communities. Higher values for surface associated communities in comparison to seawater were described earlier for seagrasses [@Ugarelli2019] and could be attributed to a larger set of inhabitable microniches existing on macrophyte surfaces. In addition, highest values observed for *Caulerpa cylindracea* are probably a consequence of sediment derived OTUs that were present only in *Caulerpa cylindracea* communities. *Caulerpa cylindracea* stolon is attached to surface sediment with rhizoids, so the stolon and rhizoids are in a direct contact with the sediment surface. Part of the surface attached *Caulerpa cylnidracea* community is therefore comprised of sediment derived cells that could cause the observed increase in richness. In addition, seasonal richness differences observed for surface attached communities showed slightly higher values in spring and summer could be explained by a higher macrophyte growth in these seasons [M. Najdek, personal communication; @Zavodnik1998; @Ruitton2005]. During active periods macrophytes exhibit a more dynamic chemical interaction with the surface community causing an opening of a larger set of microniches.

>>>>

Observed highest richness values for *Caulerpa cylindracea* (invaded and noninvaded), middle for *Cymodocea nodosa* and lowest for seawater derived communities. Higher values for surface associated communities in comparison to seawater were described earlier for seagrasses [@Ugarelli2019] and could be attributed to a larger set of inhabitable microniches existing on macrophyte surfaces. In addition, highest values observed for *Caulerpa cylindracea* are probably a consequence of sediment derived OTUs that were present only in *Caulerpa cylindracea* communities. *Caulerpa cylindracea* stolon is attached to surface sediment with rhizoids, so the stolon and rhizoids are in a direct contact with the sediment surface. Part of the surface attached *Caulerpa cylnidracea* community is therefore comprised of sediment derived cells that could cause the observed increase in richness. In addition, seasonal richness differences observed for surface attached communities showed slightly higher values in spring and summer could be explained by a higher macrophyte growth in these seasons [M. Najdek, personal communication; @Zavodnik1998; @Ruitton2005]. During active periods macrophytes exhibit a more dynamic chemical interaction with the surface community causing an extension of the microniche number.

### 2020-03-02 submission/manuscript.tex
Desulfobacterota removal checked.

Observed highest richness values for \emph{Caulerpa cylindracea}
(invaded and noninvaded), middle for \emph{Cymodocea nodosa} and lowest
for seawater derived communities. Higher values for surface associated
communities in comparison to seawater were described earlier for
seagrasses (Ugarelli \emph{et al.}, 2019) and could be attributed to a
larger set of inhabitable microniches existing on macrophyte surfaces.
In addition, highest values observed for \emph{Caulerpa cylindracea} are
probably a consequence of sediment derived OTUs that were present only
in \emph{Caulerpa cylindracea} communities. \emph{Caulerpa cylindracea}
stolon is attached to surface sediment with rhizoids, so the stolon and
rhizoids are in a direct contact with the sediment surface. Part of the
surface attached \emph{Caulerpa cylnidracea} community is therefore
comprised of sediment derived cells that could cause the observed
increase in richness. In addition, seasonal richness differences
observed for surface attached communities showed slightly higher values
in spring and summer could be explained by a higher macrophyte growth in
these seasons (M. Najdek, personal communication; Zavodnik \emph{et
al.}, 1998; Ruitton \emph{et al.}, 2005). During active periods
macrophytes exhibit a more dynamic chemical interaction with the surface
community causing an opening of a larger set of microniches.

>>>>

Observed highest richness values for \emph{Caulerpa cylindracea}
(invaded and noninvaded), middle for \emph{Cymodocea nodosa} and lowest
for seawater derived communities. Higher values for surface associated
communities in comparison to seawater were described earlier for
seagrasses (Ugarelli \emph{et al.}, 2019) and could be attributed to a
larger set of inhabitable microniches existing on macrophyte surfaces.
In addition, highest values observed for \emph{Caulerpa cylindracea} are
probably a consequence of sediment derived OTUs that were present only
in \emph{Caulerpa cylindracea} communities. \emph{Caulerpa cylindracea}
stolon is attached to surface sediment with rhizoids, so the stolon and
rhizoids are in a direct contact with the sediment surface. Part of the
surface attached \emph{Caulerpa cylnidracea} community is therefore
comprised of sediment derived cells that could cause the observed
increase in richness. In addition, seasonal richness differences
observed for surface attached communities showed slightly higher values
in spring and summer could be explained by a higher macrophyte growth in
these seasons (M. Najdek, personal communication; Zavodnik \emph{et
al.}, 1998; Ruitton \emph{et al.}, 2005). During active periods
macrophytes exhibit a more dynamic chemical interaction with the surface
community causing an extension of the microniche number.
